\newgeometry{letterpaper, margin=1in}\afterpage{\aftergroup\restoregeometry}

\setlength{\parskip}{1em}

\begin{center}
	\def\arraystretch{0.75}
	\title{Yubo Cao}\vspace{0.5em}\footnotesize\\
	\hspace{-0.5em}\begin{tabular}{c}
		GSMST                         \\
		Lawrenceville, Georgia, 30044 \\
		\phone{4708549826}            \\
		\email{cao2006721@gmail.com}  \\
	\end{tabular}\par
	\vspace{-0.7em}\hrulefill
\end{center}

Dear Hiring Manager, \bigskip

I am writing to express my interest in the CodeQuest internship at Lockheed Martin Corporation. I am fascinated by the cutting-edge technology and innovation that Lockheed Martin is known for, and I would love to contribute to the world's most challenging projects in aerospace, defense, and security.

As a current sophomore at the Gwinnett School of Mathematics, Science, and Technology (GSMST), I have a strong academic background in computer science and mathematics. I have taken Physics \& Engineering, which taught me statistical analysis, CAD/3D modeling, electrical engineering, and other relevant skills. I have also taken AP Computer Science Principles and scored a 5 on the exam. I am self-studying AP Computer Science A and will take the exam this year. My superior performance on practice exams made my teacher approve my request to take the exam directly. Additionally, I have maintained a GPA of 4.15, demonstrating my aptitude for learning and my readiness to function in a professional setting.

My primary motivation for applying for this internship is my love of programming and creating innovative solutions. Through my participation in the FIRST Tech Challenge (FTC), I have gained hands-on experience programming in Java and Kotlin, as well as working as part of a team. I have also developed an interest in artificial intelligence and machine learning, and have explored various online courses and projects on these topics. Moreover, I have participated in several competitions related to cybersecurity and algorithmic problem-solving, such as picoCTF, CyberPatriot (as a first place silver semi-finalist), and USACO (silver tier), where I have honed my skills and learned new techniques.

I am eager to apply my skills and knowledge in a professional setting, and I am committed to continuing to learn and grow in this field. I am impressed by Lockheed Martin's commitment to STEM education and diversity, and I would be honored to join such a prestigious organization. My resume is enclosed for your review as well. I look forward to hearing from you and learning more about the internship opportunity.

Thank you for your time and consideration.

\bigskip

Sincerely,

\bigskip

Yubo Cao

\newpage